\Large Bayes network classifiers for fMRI

### 2012-09-14 proposal/proposal.tex

The dataset contains data on 6 subjects that each completed a number of trials. For each trial (cf. Section~\ref{sec:setup}), a brain scan was made every 500 ms, totalling to approximately 54 scans per trial. Each scan consists of a list of approximately 5000 voxels (three dimensional pixels), of predefined regions of the brain. Along with each trial, metadata is available on the type of trial (e.g. what stimulus was shown), the result of the trial, and to which subject the scan belongs.

@@

The dataset we use originated from a project that researched classifying cognitive state using Gaussian Naive Bayes classifiers. This resulted in an accuracy of approximately 85\%. According to literature, a higher accuracy could be obtained by using a so-called \textit{Tree Augmented Naive Bayesian network classifier}, or TAN \cite{Friedman:1997gw}. We will use this classification method to investigate whether we are indeed able to reach a higher accuracy.

>>>>

The dataset contains data on 6 subjects that each completed a number of trials. For each trial (cf. Section~\ref{sec:setup}), a brain scan was made every 500 ms, totalling to approximately 54 scans per trial. Each scan consists of a list of approximately 5000 voxels (three dimensional pixels), of predefined regions of the brain. Along with each trial, metadata is available on the type of trial (e.g. what stimulus was shown), the result of the trial, and to which subject the scans belong.

@@

The dataset we use originated from a project that researched classifying cognitive state using Gaussian Naive Bayes classifiers. This resulted in an accuracy of approximately 85\%. According to literature\cite{Friedman:1997gw}, a higher accuracy could be obtained by using a so-called \textit{Tree Augmented Naive Bayesian network classifier}, or TAN. We will use this classification method to investigate whether we are indeed able to reach a higher accuracy.
